Approximation as Differentiation notes

### 2025-02-25 notes/sec/grothendieck.tex
If 𝐶 has binary products then so does Fam(𝐶).
Constructing lambda.
Corrections.

\begin{proposition}
If $C$ has products then $\Fam(C)$ has products.
\end{proposition}

@@

\begin{proof}
Suppose $X = (I, X)$ and $Y = (I, Y)$ are objects in $\Fam(C)$. Define $[X, Y]$ to be the object $(K,Z)$ in
$\Fam(C)$ where $K$ is the set of morphisms from $\Fam(I,C)$ to $\Fam(J,C)$ and $Z$ is the $K$-indexed family
which maps every $f: \Fam(I,C) \to \Fam(J,C)$ in $K$ to $\prod_{i \in I}\reindex{Y}{f}_i$. Then the following
families of morphisms in $\Fam(C)$:
\begin{enumerate}
\item $\lambda_{X,Y,Z}: \Fam(C)(X \times Y, Z) \to \Fam(C)(X, [Y, Z])$
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}

>>>>

\begin{proposition}
If $C$ has binary products then so does $\Fam(C)$.
\end{proposition}

@@

\begin{proof}
Suppose $C$ locally small with binary biproducts given by $\biprod$. Suppose $X = (I, X)$ and $Y = (I, Y)$ are
objects in $\Fam(C)$. Define $[X, Y]$ to be the object $(K,Z)$ in $\Fam(C)$ where $K$ is $\Fam(C)(X,Y)$ and
$Z$ is the $K$-indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $K$ to $\prod_{i \in
I}\reindex{Y}{f}_i$. Then define the following families of functions:

\begin{enumerate}
\item $\lambda_{X,Y,Z}$ which sends any morphism $(f: I \times J \to K, g: X \times Y \to \reindex{Z}{f}): X
\times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X \to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ where
$f'(i)(j) = f(i,j)$ and $g'(i) = $.
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}
